Mysis analysis

### 2015-09-23 results/mysisResults.Rmd
updated results

---
title: "Mysis analysis"
author: "John Tipton"
date: "September 9, 2015"
output: html_document
---
```{r loadLibraries, echo=FALSE, include=FALSE, message=FALSE}
options(digits=3)
library(knitr)
library(ggplot2)
library(Gmisc)
library(MASS)
library(stringr)
library(mgcv)
library(lme4)
```
## Model for Total counts for each net
```{r totalCount, echo=FALSE, include=FALSE, message=FALSE, cache=TRUE}
set.seed(123)
data_one_way <- read.csv("~/mysis/data/ttestData.csv", skip = 3, nrows = 40, header = TRUE)
count <- c(data_one_way$full.5,  ## count for full net
            4 * data_one_way$half.5) ## count for half net adjusted for radius
date <- rep(as.factor(data_one_way$month), 2)
station <- rep(data_one_way$Station, 2)
net <- as.factor(c(rep("full", 40), rep("half", 40)))
data <- data.frame(count=count, date=date, net=net)
X <- model.matrix(~ net * date)
ggplot(data=data, aes(count)) + geom_histogram() + facet_grid(net ~ .)
summary(nbmod <- glm.nb(y ~ . -1, data = data.frame(y=count, X)))
# summary(qpmod <- glmmPQL(count ~ net * date, random=~1|station, family=neg.bin(2.6)))
# summary(glmmPQL(count ~ net * date, random=~1|station, family=neg.bin(0.1))) 
# summary(glmmPQL(count ~ net * date, random=~1|station, family=neg.bin(10)))
coefs <- c(nbmod$coefficients, nbmod$theta)
```

@@

date <- as.factor(date)
net <- as.factor(size)
count[rep(net, times=4) == 0.5] <- count[rep(net, times=4) == 0.5] * 4
data <- data.frame(count=count, date=rep(date, times=4), net=rep(net, times=4), gender=gender)
# X <- model.matrix(~ net * date + net * gender + gender * date, data=data)
X <- model.matrix(~ net * gender + net * date + gender * date, data=data)
ggplot(data=data, aes(count)) + geom_histogram() + facet_grid(net ~ gender)
ggplot(data=data, aes(count)) + geom_histogram() + facet_grid(net ~ date)
ggplot(data=data, aes(count)) + geom_histogram() + facet_grid(gender ~ date)
nbmod <- glm.nb(y ~ . -1, data = data.frame(y=count, X))
```

@@

date <- rep(as.factor(data_one_way$month), 2)
net <- as.factor(c(rep("full", 40), rep("half", 40)))
data <- data.frame(prop=prop, date=date, net=net)
X <- model.matrix(~ net * date)
ggplot(data=data, aes(prop)) + geom_histogram() + facet_grid(net ~ .)
library(betareg)
brmod <- betareg(prop ~ . -1, data = data.frame(prop, X))
summary(brmod)
```

@@

# date <- as.numeric(data_length$Date)
# date[date == 2] <- 1      ## collapse into monthly values
# date[date == 3] <- 2
# date[date == 4] <- 3
# date <- as.factor(date)
station <- data_length$Station
# plot(as.numeric(date), type='l', main = "Is this a data error? - yes?")
## correct date mislabeling
date <- as.numeric(data_length$Date)
date[7330:7519] <- 4
date[7559:7773] <- 4
date[date == 2] <- 1      ## collapse into monthly values
date[date == 3] <- 2
date[date == 4] <- 3
date <- as.factor(date)
# plot(as.numeric(date), type='l', main = "Data looks better")
data <- data.frame(y=y, date=date, net=as.factor(net), gender=gender)
X <- model.matrix(~ net + date + gender, data=data)
levels(data$date) <- c("July", "August", "Septempber")
levels(data$net) <- c("Small Net", "Large Net")
levels(data$gender) <- c("Female", "Juvenile", "Male", "Unknown")
ggplot(data=data, aes(y)) + geom_histogram() + facet_grid(net ~ date) 
ggplot(data=data, aes(y)) + geom_histogram() + facet_grid(net ~ gender)
ggplot(data=data, aes(y)) + geom_histogram() + facet_grid(date ~ gender)
idx <- attr(uniquecombs(X), "index")
summary(lmmod <- lm(y ~ net + date * gender))
library(lme4)
# summary(lmemod <- lmer(y ~ net * date + net * gender + date * gender + (1|station)))
# summary(lmemod <- lmer(y ~ net + date * gender + (1|station)))
# summary(rlmmod <- rlm(y ~ net * date + net * gender + date * gender))
summary(rlmmod <- rlm(y ~ net + date * gender))
tvalues <- summary(rlmmod)$coefficients[, 3]
df <- summary(rlmmod)$df[2]
pvalues <- pt(abs(tvalues), df, lower.tail=FALSE) * 2
```

>>>>

---
title: "Mysis analysis"
author: "John Tipton"
date: "September 9, 2015"
output: html_document
---
```{r loadLibraries, echo=FALSE, include=FALSE, message=FALSE}
options(digits=3)
library(knitr)
library(ggplot2)
library(Gmisc)
library(MASS)
library(stringr)
library(mgcv)
library(lme4)
```
## Model for Total counts for each net
```{r totalCount, echo=FALSE, include=FALSE, message=FALSE, cache=TRUE}
set.seed(123)
data_one_way <- read.csv("~/mysis/data/ttestData.csv", skip = 3, nrows = 40, header = TRUE)
count <- c(data_one_way$full.5,  ## count for full net
            4 * data_one_way$half.5) ## count for half net adjusted for radius
date <- rep(as.factor(data_one_way$month), 2)
station <- rep(data_one_way$Station, 2)
net <- as.factor(c(rep("full", 40), rep("half", 40)))
data <- data.frame(count=count, date=date, net=net)
levels(data$date) <- c("July", "August", "Septempber")
levels(data$net) <- c("Small Net", "Large Net")
X <- model.matrix(~ net * date)
summary(nbmod <- glm.nb(y ~ . -1, data = data.frame(y=count, X)))
# summary(qpmod <- glmmPQL(count ~ net * date, random=~1|station, family=neg.bin(2.6)))
# summary(glmmPQL(count ~ net * date, random=~1|station, family=neg.bin(0.1))) 
# summary(glmmPQL(count ~ net * date, random=~1|station, family=neg.bin(10)))
coefs <- c(nbmod$coefficients, nbmod$theta)
```

```{r plotCount, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(data=data, aes(count)) + geom_histogram() + facet_grid(net ~ .) + 
  ggtitle("Histogram of normalized counts by net size")
ggplot(data=data, aes(count)) + geom_histogram() + facet_grid(net ~ date) + 
  ggtitle("Histogram of normalized counts by net size and date")
```

@@

date <- as.factor(date)
net <- as.factor(size)
count[rep(net, times=4) == 0.5] <- count[rep(net, times=4) == 0.5] * 4
data <- data.frame(count=count, date=rep(date, times=4), net=rep(net, times=4), gender=gender)
levels(data$date) <- c("July", "August", "Septempber")
levels(data$net) <- c("Small Net", "Large Net")
levels(data$gender) <- c("Female", "Juvenile", "Male", "Unknown")
# X <- model.matrix(~ net * date + net * gender + gender * date, data=data)
X <- model.matrix(~ net * gender + net * date + gender * date, data=data)

nbmod <- glm.nb(y ~ . -1, data = data.frame(y=count, X))
```

```{r plot SexCount, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(data=data, aes(count)) + geom_histogram() + facet_grid(net ~ gender) + 
  ggtitle("Histogram of normalized counts by sex and net size")
# ggplot(data=data, aes(count)) + geom_histogram() + facet_grid(net ~ date) + 
#   ggtitle("Histogram of normalized counts by net size")
ggplot(data=data, aes(count)) + geom_histogram() + facet_grid(gender ~ date) + 
  ggtitle("Histogram of normalized counts by sex and date")
```

@@

date <- rep(as.factor(data_one_way$month), 2)
net <- as.factor(c(rep("full", 40), rep("half", 40)))
data <- data.frame(prop=prop, date=date, net=net)
levels(data$date) <- c("July", "August", "Septempber")
levels(data$net) <- c("Small Net", "Large Net")
X <- model.matrix(~ net * date)
library(betareg)
brmod <- betareg(prop ~ . -1, data = data.frame(prop, X))
summary(brmod)
```

```{r plotJuviCount, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(data=data, aes(prop)) + geom_histogram() + facet_grid(net ~ .) + 
  ggtitle("Histogram of proportion of juveniles by net size")
```

@@

# date <- as.numeric(data_length$Date)
# date[date == 2] <- 1      ## collapse into monthly values
# date[date == 3] <- 2
# date[date == 4] <- 3
# date <- as.factor(date)
station <- data_length$Station
# plot(as.numeric(date), type='l', main = "Is this a data error? - yes?")
## correct date mislabeling
date <- as.numeric(data_length$Date)
date[7330:7519] <- 4
date[7559:7773] <- 4
date[date == 2] <- 1      ## collapse into monthly values
date[date == 3] <- 2
date[date == 4] <- 3
date <- as.factor(date)
# plot(as.numeric(date), type='l', main = "Data looks better")
data <- data.frame(y=y, date=date, net=as.factor(net), gender=gender)
X <- model.matrix(~ net + date + gender, data=data)
levels(data$date) <- c("July", "August", "Septempber")
levels(data$net) <- c("Small Net", "Large Net")
levels(data$gender) <- c("Female", "Juvenile", "Male", "Unknown")
idx <- attr(uniquecombs(X), "index")
summary(lmmod <- lm(y ~ net + date * gender))
library(lme4)
# summary(lmemod <- lmer(y ~ net * date + net * gender + date * gender + (1|station)))
# summary(lmemod <- lmer(y ~ net + date * gender + (1|station)))
# summary(rlmmod <- rlm(y ~ net * date + net * gender + date * gender))
summary(rlmmod <- rlm(y ~ net + date * gender))
tvalues <- summary(rlmmod)$coefficients[, 3]
df <- summary(rlmmod)$df[2]
pvalues <- pt(abs(tvalues), df, lower.tail=FALSE) * 2
```

```{r plotLength, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(data=data, aes(y)) + geom_histogram() + facet_grid(net ~ date) + 
  ggtitle("Histogram of lengths by net size")
ggplot(data=data, aes(y)) + geom_histogram() + facet_grid(net ~ gender) + 
  ggtitle("Histogram of lengths by sex and net size")
ggplot(data=data, aes(y)) + geom_histogram() + facet_grid(date ~ gender) + 
  ggtitle("Histogram of lengths by sex and date")
```
